### 2015-11-17 paper.Rmd
seems like pandoc knows what to do there anyway...
tables look less gross

---
author:
  - name: David L Miller
    affiliation: Centre for Research into Ecological and Environmental Modelling, University of St Andrews
    address: >
      The Observatory,
      St Andrews, Fife KY16 9LZ, Scotland
    email: dave@ninepointeightone.net
    url: http://converged.yt
title:
  formatted: "Distance Sampling in \\proglang{R}"
  # If you use tex in the formatted title, also supply version without
  plain:     "Distance Sampling in R"
  # For running headers, if needed
  #short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [distance sampling, abundance estimation, line transects, point transects, "\\proglang{R}"]
  plain:     [distance sampling, abundance estimation, line transects, point transects, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{longtable}
output: rticles::jss_article
bibliography: jstatsoft.bib
---

@@

\begin{table}
\caption{Modelling options for key plus adjustment series models for the detection function.}
\begin{tabular}{llll}
\hline
key function   & form   & adjustment & form\\
\hline
 uniform  & $1/w$   & cosine  & $\sum_{o=1}^O a_o \cos(o \pi y/w)$ \\
 & & Simple polynomial & $\sum_{o=1}^O a_o (y/w)^{2o}$ \\
 half-normal  & $\exp\left(-\frac{y^2}{2 \sigma^2}\right)$ & cosine  & $\sum_{o=2}^O a_o \cos(o \pi y/w)$ \\
 & & Hermite polynomial & $\sum_{o=2}^O a_o H_{2o}(y/\sigma)$ \\
 hazard-rate  & $1-\exp\left[-\left(\frac{y}{\sigma}\right)^{-b}\right]$ & cosine  & $\sum_{o=2}^O a_o \cos(o \pi y/w)$ \\
 & & Simple polynomial & $\sum_{o=2}^O a_o (y/w)^{2o}$ \\
\hline
\end{tabular}
\label{tab:keyadj}
\end{table}

@@

```{r summary-table, results="asis", echo=FALSE}
library(knitr)
kable(summarize_ds_models(amakihi_hr, amakihi_hr_obs, amakihi_hr_obs_mas),
      digits = 3, format = "latex", row.names = FALSE, escape=FALSE,
      caption="Summary for the detection function models fitted to the amakihi data. \"C-vM\" stands for Cramer-von Mises, $P_a$ indicates average detectability (see \"Estimating abundance and variance\"), se indicates standard error. Models are sorted according to AIC.\\label{tab:amakihi}")
```

@@

```{r minke-abundance-table}
minke_table <- summary(minke_hn)$dht$individuals$N
minke_table$lcl <- minke_table$ucl <- minke_table$df <- NULL
colnames(minke_table) <- c("Stratum", "$\\hat{N}$", "$\\text{se}(\\hat{N}$)", 
                           "$\\text{CV}(\\hat{N}$)")
kable(minke_table, digits = 3, format = "latex",
      row.names = FALSE, escape=FALSE,caption="Summary of abundance estimation for the half-normal model for the minke whale data.\\label{minke-abund}")
```

@@

>>>>

---
author:
  - name: David L Miller
    affiliation: Centre for Research into Ecological and Environmental Modelling, University of St Andrews
    address: >
      The Observatory,
      St Andrews, Fife KY16 9LZ, Scotland
    email: dave@ninepointeightone.net
    url: http://converged.yt
title:
  formatted: "Distance Sampling in \\proglang{R}"
  # If you use tex in the formatted title, also supply version without
  plain:     "Distance Sampling in R"
  # For running headers, if needed
  #short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [distance sampling, abundance estimation, line transects, point transects, "\\proglang{R}"]
  plain:     [distance sampling, abundance estimation, line transects, point transects, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{longtable}
  \usepackage{booktabs}
output: rticles::jss_article
bibliography: jstatsoft.bib
---

@@

\begin{table}
\caption{Modelling options for key plus adjustment series models for the detection function.}
\begin{tabular}{llll}
\hline
Key function   & Form   & Adjustment series & Form\\
\hline
 Uniform  & $1/w$   & cosine  & $\sum_{o=1}^O a_o \cos(o \pi y/w)$ \\
 & & Simple polynomial & $\sum_{o=1}^O a_o (y/w)^{2o}$ \\
 Half-normal  & $\exp\left(-\frac{y^2}{2 \sigma^2}\right)$ & cosine  & $\sum_{o=2}^O a_o \cos(o \pi y/w)$ \\
 & & Hermite polynomial & $\sum_{o=2}^O a_o H_{2o}(y/\sigma)$ \\
 Hazard-rate  & $1-\exp\left[-\left(\frac{y}{\sigma}\right)^{-b}\right]$ & cosine  & $\sum_{o=2}^O a_o \cos(o \pi y/w)$ \\
 & & Simple polynomial & $\sum_{o=2}^O a_o (y/w)^{2o}$ \\
\hline
\end{tabular}
\label{tab:keyadj}
\end{table}

@@

```{r summary-table, results="asis", echo=FALSE}
library(knitr)
kable(summarize_ds_models(amakihi_hr, amakihi_hr_obs, amakihi_hr_obs_mas),
      digits = 3, format = "latex", row.names = FALSE, escape=FALSE,
      booktabs=TRUE,
      caption="Summary for the detection function models fitted to the amakihi data. ``C-vM'' stands for Cramer-von Mises, $P_a$ indicates average detectability (see ``Estimating abundance and variance''), se indicates standard error. Models are sorted according to AIC.\\label{tab:amakihi}")
```

@@

```{r minke-abundance-table}
minke_table <- summary(minke_hn)$dht$individuals$N
minke_table$lcl <- minke_table$ucl <- minke_table$df <- NULL
colnames(minke_table) <- c("Stratum", "$\\hat{N}$", "$\\text{se}(\\hat{N}$)", 
                           "$\\text{CV}(\\hat{N}$)")
kable(minke_table, digits=3, format="latex", booktabs=TRUE,
      row.names=FALSE, escape=FALSE,caption="Summary of abundance estimation for the half-normal model for the minke whale data.\\label{minke-abund}")
```

@@

# Bibliography
